The responses of \textit{\textit{Spinifex littoreus}} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2021-01-03 drafts/Response letter.md

January 3st, 2020

Editor-in-Chief
*Ecoscience*

Dear Dr. Hugo Asselin,

We thank the two anonymous reviewers for their thoughtful and useful comments on our previous manuscript (TECO-2020-0114) and we are pleased to resubmit this revised version for potential publication in *Ecoscience*. We have carefully followed the reviewers' suggestions as well as your editorial concerns, in conducting our revision. We now re-analysised the data and nearly rewrote the manuscript in response to reviewers' major concerns, the main points that have been changed in the new version are:

@@

- We have significantly streamlined the manuscript to make it more focused on our main findings now.
- We have re-analysed the data to ensure that the methods and results are more reliable and that the significance levels and error criteria have been chosen in line with international practice.
- We have revised the presentation of the manuscript to make our experimental approach more understandable.

We have also addressed all the other questions and comments raised by the two reviewers. A detailed response to each question and each comment from the reviewers is attached to this cover letter.

We trust that this new version will satisfy both you and the reviewers. Thank you once again for the time that you and reviewers have spent reviewing this MS.

The manuscript includes 1 text (3915 words), 9 figures, 40 references and one table.

@@

***[Reviewer #1 Comment #2]*** Line 116: Figure 1. is the third Figure, mentioned in the text, so I think it would be better to renumber it to Figure 3. and renumber the other Figures accordingly.
***[Response]*** Since we re-analyzed our data, we have re-organized manuscript with figures where numbers are well renumbered.

***[Reviewer #1 Comment #3]*** Lines 117-119: Can you provide a reference, that concerns flora and/or vegetation of nebkhas/foredunes in the area?
***[Response]*** We added some new cites in the proper position of ms now (e. g. (Yang et al. 2017, Divyasree & Raju 2019)) to describe the vegetation in this area.

***[Reviewer #1 Comment #4]*** Line 125: How did you compare the age of different plants?
***[Response]*** Thanks for pointing this out. In fact, we only compare them by size (we mis-wrote in the last version.).

***[Reviewer #1 Comment #5]*** Lines 127-129: Did you measure the height of vertical ramets and the length of stolons to know they were all similar with each other before choosing the plants for the study?
***[Response]*** Yes, we started our measurements in the first day of experiment and we show them in the figures now [**see Figure 5**].

@@

***[Reviewer #1 Comment #7]*** Lines 269-272: This sentence is not clear to me.
***[Response]*** Thanks for pointing this out, we have deleted this unclear sentence.

***[Reviewer #1 Comment #8]*** Although I'm not a native English speaker, I believe that English should be improved. I wouldn't say it is poor but it needs to be revised. Some examples:
Lines 28-29: Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, …
Line 57: The tolerance capacity to different sand burial levels is varied among species, …
Lines 142-143: Since the height of vertical ramets of S. littoreus is relatively high, it is usually impossible for them to be completely buried in the sand.
***[Response]*** Thanks for the valuable comment, this has been clarified in the revised version of the manuscript.

### References

Divyasree, M. & A. J. S. Raju, 2019. An Ecological Study Of Reproduction In Spinifex Littoreus (Burm.F.) Merr. (Poaceae), A dominant species of sand dune ecosystem along the visakhapatnam coast, andhra pradesh. Journal of Palynology, 55: 35–54.

### 2021-01-03 tex/interactcsesample.tex
update response letter

During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape. Considering the uncovering and re-covering of sand will probably affect the gravity signal of plants to sand burial, we finished our measurements in minutes to minimize the potential disturbance, and re-covered the plants to the previous sand burial level with same sand. When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label on the stolons. Then all the samples were taken back to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of $65^{\circ}C$ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).

>>>>

During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape. Considering the uncovering and re-covering of sand will probably affect the gravity signal of plants to sand burial, we finished our measurements in a very short time period (usually 3-5 minutes compared with days of interval) to minimize the potential disturbance, and re-covered the plants to the previous sand burial level with same sand. When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label on the stolons. Then all the samples were taken back to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of $65^{\circ}C$ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).
